On Secure Delegation of SampBQP with a Classical Client

### 2020-02-22 qpip0.tex
Change autoref to cref

Here we combine \autoref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients. Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.

@@

\begin{protocol}{Mahadev's 4 round commitment}
\label{proto:urmila4}
\begin{enumerate}
    \item Verifier $\bbV$ is a classical machine. Prover $\bbP$ is a $\BQP$ machine. 
%    \item Both the verifier and the prover know a $\BQP$ circuit $C$ and an input string $x$.
    \item Both party know the number of qubits $n$ and a security parameter $\lambda=o(n)$.
    \item Verifier has a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit. If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.  
    \item In the first round, the verifier generate a secret key and  public key pair $(sk,pk)$ from $h$ and $\lambda$ and sent $pk$ to the prover.
    \item In the second round, the prover pick some $n$-qubit quantum state $\rho$ and generate a "commitment" $y$ from $pk$ and $\rho$. He send $y$ to the verifier and keep the leftover quantum state $\sigma$.
    \item In the third round, the verifier send a uniformly random challenge bit $c\in \{0,1\}$. The prover needs to do a "Testing round" if $c=0$. The prover needs to do a "Hadamard round" if $c=1$.
    \item In the fourth round. The prover generates a classical string $a$ from $c$ and $\sigma$ and send to back to the prover.
    \item If $c=0$, the verifier decides whether he is going to reject from $(pk,a,y)$. If $c=1$ the verifier computes an $n$-bit string $z$ from $(sk,h,y,a)$.
\end{enumerate}
\end{protocol}

\begin{lemma}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
\label{proto:QPIP0samp}
\begin{enumerate}
%    \item Verifier start with description of quantum circuit $C$, input string $x$ 
    \item Both verifier and prover start with the description of number of qubits $n$, quantum circuit $C$, input string $x$, and  a soundness parameter $\varepsilon$.
    \item Run $m=O(1/\varepsilon)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications. On the second round, for each copy, the prover choose the state specified by Protocol~\ref{ProtoQPIP1}  (with error $\eps$) as $\rho$. On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies.
    \item \label{step:multi-testing}Verifier rejects if the results on any of the test rounds is rejected. 
    \item If all testing rounds are accepted, verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
\end{enumerate}
\end{protocol}

\begin{theorem}\label{thm:urmila-binding}
    Protocol~\ref{proto:QPIP0samp} is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and $\eps$ computational soundness error\hannote{definition}. 
\end{theorem}

@@

\begin{proof}

 [[Partition lemma -> Parallel repetition]], except for probability $\eps$, either the verifier reject at step~\ref{step:multi-testing} or $z$ is $\negl(n)$-computationally indistinguishable to $M_{XZ}(\rho,h)$ by Theorem~\ref{thm:urmila-binding}.

 By theorem~\ref{QPIP1thm}, $M_{XZ}(\rho,h)$  $\eps$-close to $C(x)$. Therefore\hannote{?}, $M_{XZ}(\rho,h)$  and  $C(x)$ $z$ are $\eps$-Q-computationally indistinguishable, and thus $z$ and $C(x)$ are  $2\eps$-Q-computationally indistinguishable.

\end{proof}
===========

@@

%$\frac{\gamma_0}{T}=1/\poly(\secpar)$
\begin{lemma}[partition lemma]\label{lem:partition}
Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}.  Let $i\in[m]$, 
$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$. Let $\gamma$ be a random number sampled uniformly from $\L[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R]$.

>>>>

Here we combine \cref{QPIP1thm} with results from \cite{FOCS:Mahadev18a} to create a delegation protocol for $\SampBQP$ for fully classical clients. Combining them will cost polynomially rounds, so we use results from \cite{parallelrep} that allows parallel repetition to construct a constant-round protocol.

@@

\begin{protocol}{Mahadev's 4 round commitment}
\label{proto:urmila4}
\begin{enumerate}
    \item Verifier $\bbV$ is a classical machine. Prover $\bbP$ is a $\BQP$ machine. 
%    \item Both the verifier and the prover know a $\BQP$ circuit $C$ and an input string $x$.
    \item Both party know the number of qubits $n$ and a security parameter $\lambda=1^{\poly(n)}$.
    \item Verifier has a string $h \in \{0,1\}^n$ that specifies the measurement he wants to make: if $h_i=0$, he wants a $X$ measurement on $i$-th qubit. If $h_i=1$, he wants a $Z$ measurement on $i$-th qubit.  
    \item In the first round, the verifier generate a secret key and  public key pair $(sk,pk)$ from $h$ and $\lambda$ and sent $pk$ to the prover.
    \item In the second round, the prover pick some $n$-qubit quantum state $\rho$ and generate a "commitment" $y$ from $pk$ and $\rho$. He send $y$ to the verifier and keep the leftover quantum state $\sigma$.
    \item In the third round, the verifier send a uniformly random challenge bit $c\in \{0,1\}$. The prover needs to do a "Testing round" if $c=0$. The prover needs to do a "Hadamard round" if $c=1$.
    \item In the fourth round. The prover generates a classical string $a$ from $c$ and $\sigma$ and send to back to the prover.
    \item If $c=0$, the verifier decides whether he is going to reject from $(pk,a,y)$. If $c=1$ the verifier computes an $n$-bit string $z$ from $(sk,h,y,a)$, $z=V_f(sk,h,y,a)$.
\end{enumerate}
\end{protocol}

\begin{definition}
With loss of generality,  we can assume that the testing round verification is deterministic. We denote the set of strings $a$ accepted by the verifier in the testing round with $(pk,y)$ as $\Acc_{pk,y}$.
\end{definition}

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that $z$ is computationally indistinguishable with $\negl(n)$ error \hannote{add notation for comp indist.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

@@

\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
\label{proto:QPIP0samp}
\begin{enumerate}
%    \item Verifier start with description of quantum circuit $C$, input string $x$ 
    \item Both verifier and prover start with the description of number of qubits $n$, quantum circuit $C$, input string $x$, and  a soundness parameter $\varepsilon$.
    \item Run $m=O(1/\varepsilon^2)$ copies of protocol~\ref{proto:urmila4} in parallel, with following modifications. The copies share the same $h$ but have separate $\{sk\}$, $\{pk\}$, $\{y\}$, $\{c\}$, and $\{a\}$.  The prover use $h$ specifier by step~\ref{} of Protocol~\ref{ProtoQPIP1} to generate $\{sk\}$ and $\{pk\}$ for all copies on the first round. On the second round, for each copy, the prover choose the state specified by step~\ref{} of Protocol~\ref{ProtoQPIP1}  (with  $(C,x,\eps)$ as input) as $\rho$. On the third round, the verifier uniformly randomly pick an $i\in [m]$, do a Hadamard round on $i$-th copy, and has do test rounds on all other copies, i.e. $c_i=1$ and $c_j=0$ for all $j\neq i$.
    \item \label{step:multi-testing}Verifier rejects if the result on any of the test rounds is rejected. 
    \item If all testing rounds are accepted, verifier run the verification procedure of Protocol~\ref{ProtoQPIP1} on the string $z$ decoded from the Hadamard round.
\end{enumerate}
\end{protocol}

\begin{theorem}\label{thm:qpip0}
    Protocol~\ref{proto:QPIP0samp} is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and $\eps$ computational soundness error\hannote{definition}. 
\end{theorem}

@@

%Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$.
\begin{lemma}[partition lemma2]\label{lem:partition2}
Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round. Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$.  Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.

 For all $i\in[m]$, $\gamma \in \L\{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}\R\}$, there exist two efficient quantum circuit $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ such that for all (possibly sub-normalized)  quantum state $\ket{\psi}_{\regX,\regZ}$,

\begin{align}
    G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{0,i,\gamma}}_{\regX,\regZ} \\ G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ} \defeq& \ket{\psi_{1,i,\gamma}}_{\regX,\regZ}  \\
    \ket{\psi}_{\regX,\regZ} =&   \ket{\psi_{0,i,\gamma}}_{\regX,\regZ}+ \ket{\psi_{1,i,\gamma}}_{\regX,\regZ}+\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}
\end{align}

% $$ \ket{\psi}_{\regX,\regZ} =  G_{0,i,\gamma}\ket{\psi}_{\regX,\regZ}+ G_{1,i,\gamma}\ket{\psi}_{\regX,\regZ}+\ket{\psi_{err}}_{\regX,\regZ},$$

  Note that $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ has failure probabilities, and this is reflected by the fact that $\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}$ and $\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}$ are  sub-normalized. $G_{0,i,\gamma}$ and $G_{1,i,\gamma}$ depend on $(U_0,U)$.

Furthermore, the following properties are satisfied for all $i\in[m]$.
%
\begin{enumerate}
    \item \label{property:partition-err}  $$E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\|^2 \leq \frac{6}{T}+\negl(n),$$

    where the averaged is over uniformly sampled $\gamma$. This also implies
    \begin{align}
        E_{\gamma}\|\ket{\psi_{err,i,\gamma}}_{\regX,\regZ}\| \leq \sqrt{\frac{6}{T}}+\negl(n)
    \end{align}
by Cauchy's inequality.

        \item \label{property:partition-testing}
For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and  $j\neq i$, we have

%      \begin{align*}
%  \Pr\left[M_{\regX_i}\circ U\frac{\ket{\{c\}}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{pk_i,y_i}\right]\leq (m-1)\gamma+\negl(\secpar).
%  \end{align*}

%  Define
%  $$\ket{\widetilde{\psi_{0,i,\gamma}}}\defeq U\frac{\ket{\{c\}}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}.$$
%  We have
%  \begin{align}
%      \vev{\widetilde{\psi_{0,i,\gamma}}|P_{i,pk_i,y_i,acc}|\widetilde{\psi_{0,i,\gamma}}} \leq (m-1)\gamma+\negl(\secpar),
%  \end{align}
 \begin{align}
    \norm{ P_{i,pk_i,y_i,acc} \circ U\frac{\ket{e_j}_{\regC}\ket{\psi_{0,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}}^2 \leq (m-1)\gamma_0+\negl(\secpar),
 \end{align}

where $P_{i,pk_i,y_i,acc}$ are projector to the states that $i$-th testing round accepts with $pk_i,y_i$, including the last measurement the prover did before sending $\{a\}$.  This means that $\ket{\psi_{0,i,\gamma}}$ is rejected by $i$-th testing round with high probability.

    \item \label{property:partition-binding}

    % $\{c\}\in S_m$ such that $c_i = 0$
For all $\{pk\}$, $\{y\}$, fixed $\gamma$, and $j\neq i$, there exists an efficient quantum algorithm $\ext_i$ such that

\begin{align}
     \norm{P_{i,pk_i,y_i,acc} \circ \ext_i\left(\frac{\ket{e_j}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)}^2 =1-\negl(\secpar).
\end{align}

% \begin{align*}  
%   \Pr\left[M_{\regX_i}\circ \ext_i\left(\frac{\ket{\{c\}}_{\regC}\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{pk_i,y_i}\right]=1-\negl(\secpar).
%   \end{align*}
This will imply that    $\ket{\psi_{1,i,\gamma}}$ is binding to $i$-th Hadamard round.

\item \label{property-partition-norm-sum}
  For all $\gamma$, 
  \begin{align}
    \norm{\ket{\psi_{0,i,\gamma}}}^2+ \norm{\ket{\psi_{1,i,\gamma}}}^2 \leq  \norm{\ket{\psi}}^2 
\end{align}

\item \hannote{added by me..not needed?}

$$\vev{\psi_{0,i,\gamma}|\psi_{1,i,\gamma}} = \negl(n)$$

\end{enumerate}
\end{lemma}

% \begin{proof}
% Step~\ref{step:sum-ob}: 
% \begin{align}
%   ( G_{0,i,\gamma}+G_{1,i,\gamma}) \ket{\psi}_{\regX,\regZ}
%   &= \ket{\psi_{0,i,\gamma}}_{\regX,\regZ}+\ket{\psi_{1,i,\gamma}}_{\regX,\regZ}
% \end{align}
% \end{proof}

We also need the following technical lemma.
\begin{lemma}\label{lem:samp-tech}
For any state $\ket{\psi}$,  $\ket{\phi}$ and projectors $\{P_z\}$ such that $\sum_z P_z \leq Id$ and $P_z P_{z'} =0 $ for all $z\neq z'$, we have
$$  \sum_z |\vev{\psi|P_z|\phi}| \leq \norm{\psi}\norm{\phi} $$
\end{lemma}
\begin{proof}
\begin{align}
    \sum_z |\vev{\psi|P_z|\phi}| =&\sum_z|\vev{\psi|P_zP_z|\phi}| \nn \\
    \leq& \sum_z \norm{\bra{\psi}P_z} \norm{ P_z\ket{\phi}}  \nn \\ \leq&  \sqrt{\sum_z \norm{P_z\ket{\psi}}^2} \sqrt{\norm{ P_z\ket{\phi}}^2}     \nn \\
    \leq& \sqrt{\norm{\sum_z P_z\ket{\psi}}^2 } \sqrt{\norm{\sum_z P_z\ket{\phi}}^2 } \nn \\
    \leq & \norm{\ket{\psi}}\norm{\ket{\phi}},
\end{align}
where we used Cauchy's inequality on the second and third line and $P_z P_{z'} =0 $ on the fourth line.
\end{proof}

Now we are ready to prove Theorem~\ref{thm:qpip0}
\begin{proof}
We begin by considering the state $\ket{\psi}$ the prover in Protocol~\ref{proto:QPIP0samp} hold before he receives $\{c\}$. We denote the corresponding Hilbert space as $H_{\regX,\regZ}$.

For all $k\leq m$, $d\in \zo^k$, and $\ket{\psi} \in H_{\regX,\regZ}$, define

$$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma}G_{d_{k-1},k-1,\gamma}\cdots G_{d_2,2,\gamma} G_{d_1,1,\gamma} \ket{\psi}$$

By Lemma~\ref{lem:partition2}, we have

\begin{align} \label{eq:partition-string}
    \ket{\psi} =& \ket{\psi_{0,\gamma}}+\ket{\psi_{1,\gamma}}+\ket{\psi_{err,1,\gamma}} \nn \\
    =& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{11,\gamma}}+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}} \nn \\
    =& \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{m-1}0,\gamma}}+\ket{\psi_{1^{m-1}1,\gamma}} \nn \\
    &+\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,m,\gamma}}, 
\end{align}

where we abuse the notation and use $\ket{\psi_{err,i,\gamma}}$ to denote the error state we get from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.

By Property~\ref{property-partition-norm-sum} of Lemma~\ref{lem:partition2}, we have
\begin{align} \label{eq:bad-term-sum}
    \norm{\ket{\psi}}^2 \geq& \norm{\ket{\psi_{0,\gamma}}}^2+\norm{\ket{\psi_{1,\gamma}}}^2 \nn \\
    \geq& \norm{\ket{\psi_{0,\gamma}}}^2+
    \norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{11,\gamma}}}^2 \nn \\
    \geq& \norm{\ket{\psi_{0,\gamma}}}^2+
    \norm{\ket{\psi_{10,\gamma}}}^2+ \norm{\ket{\psi_{110,\gamma}}}^2 +\cdots  \nn \\
    &+ \norm{\ket{\psi_{1^{m-1}0,\gamma}}}^2+ \norm{\ket{\psi_{1^{m-1}1,\gamma}}}^2
\end{align}

Denote the projector in $H_{\regX,\regZ}$ corresponding to outputting string $z$ when doing Hadamard on $i$-th copy as

$$P_{acc,i,z}.$$
Note that $P_{acc,i,z}$ also depends on $\{\pk\},\,\{y\}$ and  $(sk_i,h_i,y_i)$ since it includes the measurement the prover did before sending $a$,  verifier's checking on $(m-1)$ copies of testing rounds, and  the verifier's final computation from $(sk_i,h_i,y_i,a_i)$.

Since the verifier only accepts if all $(m-1)$ copies of testing rounds accepts, for all $j\neq i$,

$$P_{acc,i,z}=P_{acc,i,z}P_{j,pk_j,y_j,acc}.$$

And therefore by Property~\ref{property:partition-testing} of Lemma~\ref{lem:partition2}, we have that for all $j <i-1$\hannote{problem with $e_j$ or $e_i$}

\begin{align} \label{eq:rejected-d}
    \norm{P_{acc,i,z} U \ket{e_i, \psi_{1^j0,\gamma}}}^2
    =& \norm{P_{acc,i,z}P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
    \leq& \norm{P_{j,pk_j,y_j,acc} U \ket{e_i}\, G_{0,j+1,\gamma}\ket{\psi_{1^j,\gamma}}  }^2 \nn \\
    \leq& (m-1)\gamma_0+\negl(n) 
\end{align}

Denote the string $0^{i-1}10^{m-i} \in \zo^m $ as $e_i$. The output string corresponding to $\ket{\psi} \in H_{\regX,\regZ}$ when $c=e_i$ is then

$$z_i\defeq \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$
where $\ket{e_i,\psi}=\ket{e_i}_\regC\ket{\psi}_{\regX,\regZ}$ and $U$ is the unitary the prover applies on the last round.

Since $\{c\}$ is drawn  from $e_i$ with uniformly random $i\in [m]$, we have 
$$ z=\frac{1}{m} \sum_i z_i= \frac{1}{m} \sum_i \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi},$$ 
where we represent the random variable $z$ as a real non-negative diagonal matrix, with the matrix entries begin probabilities. Note that $z$ is "sub-normalized", i.e. $\tr (z)= \text{probability of getting accepted} \leq 1$.

Define

\begin{align}
    z_{good,i}=E_\gamma \sum_z \proj{z} \cdot \vev{e_i,\psi_{1^{i-1}1,\gamma}|U^\dag P_{acc,i,z} U|e_i,\psi_{1^{i-1}1,\gamma}}
\end{align}

Splitting $\ket{\psi}$ with Equation~\ref{eq:partition-string}, 
%\hannote{gamma..}

\begin{align}
    \ket{\psi}=& \L. \ket{\psi_{0,\gamma}}+\ket{\psi_{10,\gamma}}+\ket{\psi_{110,\gamma}}+\cdots+\ket{\psi_{1^{i-1}0,\gamma}}+
    \ket{\psi_{1^{i-1}1,\gamma}} \R. \nn \\
     +& \L.\ket{\psi_{err,1,\gamma}}+\ket{\psi_{err,2,\gamma}}+\cdots+\ket{\psi_{err,i,\gamma}}\R. \nn \\
     =& \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
\end{align}

we have

\begin{align}
    z_i =& \sum_z \proj{z} \cdot \vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi} \nn \\
    =& \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}} +\bra{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} \R]U^\dag  P_{acc,i,z} U\nn \\
    &\L[ \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}\R]  \nn \\
    =& E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}} +\bra{\psi_{1^i,\gamma}} +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} \R]U^\dag  P_{acc,i,z} U\nn \\
    &\L[ \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}\R]  \nn \\
    =& z_{good,i}+ E_\gamma \sum_z \proj{z} \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
    \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \nn \\
      +&  \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
    +& \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} 
    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \nn \\
    +&\L.\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R] , \nn     
    %=& z_{good,i} +(\text{terms with } \psi_{1^j0},\, j\neq i ) + (\text{terms with } \psi_{1^{i-1}0}) +(\text{terms with }err ) 
\end{align}

%  U^\dag  P_{acc,i,z}U

% \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} 
% \ket{\psi_{1^i,\gamma}} 
% \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}

 where we omitted writing out $e_i$ starting the second line.  We have
\begin{align} \label{eq:zi-zgoodi}
    &\tr|z_i-z_{good,i}|   \nn \\
    \leq&  \sum_z  \L| E_\gamma \L[\sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U   \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}+
    \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}}  \R. \R. \nn \\
      +&  \sum_{k=0}^{i-1} \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}}
    +\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \nn \\
    +& \sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U  \sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} 
    +\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \nn \\
    +&\L.\L.\sum_{k=1}^{i}\bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}} \R]\R| \nn \\  %%%%%%%%%%%
    \leq&  \sum_z   E_\gamma \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^j0,\gamma}} \R|+
    2 \sum_{k=0}^{i-1} \L|\bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R.  \nn \\
      +&  2 \sum_{k=0}^{i-1}\sum_{j=1}^{i}\L| \bra{\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U\ket{\psi_{err,j,\gamma}}\R|    
    +2 \sum_{j=1}^{i}\L|\bra{\psi_{1^i,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \nn \\
    +&\L. \sum_{k=1}^{i}\sum_{j=1}^{i}\L| \bra{\psi_{err,k,\gamma}} U^\dag  P_{acc,i,z}U \ket{\psi_{err,j,\gamma}}\R| \R] \nn \\ %%%%%%%%%
      \leq&  \sum_z   \L[\sum_{k=0}^{i-1} \sum_{j=0}^{i-1} \L| \bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{e_i,\psi_{1^j0,\gamma}} \R|+
    2 \sum_{k=0}^{i-1} \L|\bra{e_i,\psi_{1^k0,\gamma}}U^\dag  P_{acc,i,z}U \ket{e_i,\psi_{1^i,\gamma}} \R|  \R]    +O\L(\frac{m^2}{\sqrt T}\R)\nn \\ %%%%%%%%%
    \leq&  \sum_z   \L[\L| \bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U    \ket{\psi_{1^{i-1}0,\gamma}} \R|+
    2  \L|\bra{\psi_{1^{i-1}0,\gamma}}U^\dag  P_{acc,i,z}U \ket{\psi_{1^i,\gamma}} \R|  \R]    \nn \\ +&O\L(\frac{m^2}{\sqrt T}+m^2{(m-1)\gamma_0}+m\sqrt{(m-1)\gamma_0}\R)\nn \\ %%%%%%%%% 
    \leq& \norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R),
\end{align}
where on the second inequality we used triangle inequality, on the third inequality we used  Lemma~\ref{lem:samp-tech} and property~\ref{property:partition-err} of Lemma~\ref{lem:partition2}, on the fourth inequality we used Lemma~\ref{lem:samp-tech} and Equation~\ref{eq:rejected-d}, and on the last inequality we used Lemma~\ref{lem:samp-tech}. Once again, we omit $e_i$ when it is not relevant.

% \begin{align}
%     &\vev{e_i,\psi|U^\dag P_{acc,i,z} U|e_i,\psi} \nn \\
%     =& \bra{e_i, \psi_{1^{i-1}1,\gamma}} U^\dag P_{acc,i,z} U \ket{e_i\psi_{1^{i-1}1,\gamma}} +\hannote{poly terms?}+ \negl(n)
% \end{align}

Now we try to  put together all $i\in [m]$. Define
$$z_{good}\defeq \frac{1}{m}\sum_i z_{good,i}.$$

We have 
\begin{align}
    \tr|z-z_{good}| =& \tr\L|\frac{1}{m}\sum_i (z_i-z_{good,i})\R| \nn \\
    \leq&  \frac{1}{m}\sum_i\tr| (z_i-z_{good,i})| \nn \\
    \leq&  \frac{1}{m}\sum_i\L[\norm{\ket{\psi_{1^{i-1}0,\gamma}}}^2+ 2\norm{\ket{\psi_{1^{i-1}0,\gamma}}}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)\R] \nn \\%%%%%%%%
    \leq&  \frac{1}{m}+ 2\frac{1}{\sqrt m}+O\L(\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R) \nn \\ %%%%%
    =&O\L( \frac{1}{\sqrt m}+\frac{m^2}{\sqrt T}+m\sqrt{(m-1)\gamma_0}\R)
\end{align}

where we used triangle inequality on the second line, Equation~\ref{eq:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.

===

%Prove that $z_{good}$ is binding.
We now proceeds to prove that $z_{good}$ is binding. I.e. there exist a $n$-qubit quantum state $\rho$ such that $z_{good}$ is $\eps$-Q-computationally indistinguishable to $\sum_z \proj{z} \tr\L(\rho \sigma_h \R)$.
\hannote{add notation for pauli matrix $\sigma_h$.}

===

 [[Partition lemma ->  Parallel repetition]], except for probability $\eps$\hannote{$\frac{1}{poly}$?}, either the verifier reject at step~\ref{step:multi-testing} or $z$ is $\negl(n)$-computationally indistinguishable to $M_{XZ}(\rho,h)$ by Lemma~\ref{lem:urmila-binding}.

 By theorem~\ref{QPIP1thm}, $M_{XZ}(\rho,h)$  $\eps$-close to $C(x)$. Therefore, $M_{XZ}(\rho,h)$  and  $C(x)$ $z$ are $\eps$-Q-computationally indistinguishable, and thus $z$ and $C(x)$ are  $2\eps$-Q-computationally indistinguishable.

\end{proof}

===========

\hannote{below are unused old fragments}

===========

@@

%$\frac{\gamma_0}{T}=1/\poly(\secpar)$
\begin{lemma}[partition lemma]\label{lem:partition}
Let $(U_0,U)$ be a prover's strategy in Protocol~\ref{proto:QPIP0samp}, where $U_0$ is the how the prover generates answer in the second round, and $U$ is how the prover generates answer in the fourth round. Let $S_m$ be sets of $\{c\}$ such that only one of the $c_i=1$. Let $\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\gamma_0=1/\poly(n)$ and $T=\poly(n)$.
